---
title: "SD"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyverse)
```
### Excercise 1
```{r}
RI_values <- read.csv("~/Downloads/RI_values.csv")

```
```{r}
RI_values %>% subset(RI_values$Compound.Name == '[11005] myristic acid [16.887]') -> subset_RI

```
```{r}
ggplot(subset_RI, aes(x=Retention.index)) + geom_histogram(bins = 15)
```

The shape of distribution:
  mildly skewed but not sufficient data points
since n is 227 , greater than 30, as per CLT, it is reasonable to state that the data follows normal distribution.


### Excercise 2



```{r}
mean (as.vector(subset_RI$Retention.index))
sd(as.vector(subset_RI$Retention.index))
```

```{r}
RI <- subset_RI$Retention.index
n_tbl <- tibble(n5 = vector(),n10 = vector(),n15 = vector(),n20 = vector(),n30 = vector(),n50 = vector())
for (i in seq(1:1000)){
  n_tbl%>%
    add_row(n5=mean(sample(RI,size = 5)),
            n10=mean(sample(RI,size = 10)),
            n15=mean(sample(RI,size = 15)),
            n20=mean(sample(RI,size = 20)),
            n30=mean(sample(RI,size = 30)),
            n50=mean(sample(RI,size = 50))) ->n_tbl
}
```

```{r}
#Convert to long form
n_tbl %>%
  pivot_longer(everything(), names_to = "sample_size", values_to = "Sample_Means") -> n_long_tbl
```
#Plot all sample mean distributions

```{r}

#levels(n_long_tbl$sample_size) <- c("n5", "n10", "n15", "n20", "n30", "n50")
n_long_tbl %>%
  ggplot(aes(x=Sample_Means)) +
  geom_histogram(fill="blue", color="black", bins = sqrt(nrow(n_long_tbl))) +
facet_wrap(facets = vars(factor(sample_size, levels = c("n5", "n10","n15", "n20","n30", "n50"))))
 
```




As the sample size increases, the std deviations decreases resulting in histograms that are more narrower and more closely resembles the normal distribution.



```{r}
n_long_tbl %>% 
group_by(sample_size) %>%
summarise_at(vars('Sample_Means'),list(Value = mean)) -> mean_summary

n_long_tbl %>% 
group_by(sample_size) %>%
summarise_at(vars(`Sample_Means`),list(Value = sd)) -> sd_summary

```

The values are close to what we expected from the graph


#Excersise 3
```{r}
RI_values %>% subset(RI_values$Compound.Name == '[1004] phosphoric acid [9.966]') -> df3

```

```{r}
ggplot(df3, aes(x=Retention.index)) + geom_histogram(bins = 15)
```

It is a skewed left distribution in which the tail is to the left and is unimodal.
Non-symmetric distribution and not a normal distribution

# Excercise 4
```{r}
mean (as.vector(df3$Retention.index))
sd(as.vector(df3$Retention.index))
```

```{r}
RI <- df3$Retention.index
random_tbl <- tibble(n5 = vector(),n10 = vector(),n15 = vector(),n20 = vector(),n30 = vector(),n50 = vector())
for (i in seq(1:1000)){
  random_tbl%>%
    add_row(n5=mean(sample(RI,size = 5)),
            n10=mean(sample(RI,size = 10)),
            n15=mean(sample(RI,size = 15)),
            n20=mean(sample(RI,size = 20)),
            n30=mean(sample(RI,size = 30)),
            n50=mean(sample(RI,size = 50))) ->random_tbl_mean_2
}
```

```{r}
#Convert to long form
random_tbl_mean_2 %>%
  pivot_longer(everything(), names_to = "sample_size", values_to = "Sample Means") -> random_long_tbl_mean_2
```

```{r}
temp <- random_long_tbl_mean_2$`Sample Means`


random_long_tbl_mean_2 %>%
  ggplot(aes(x=temp)) +
  geom_histogram(fill="blue", color="black", bins = sqrt(nrow(random_long_tbl_mean_2))) +
  facet_wrap(facets = vars(factor(sample_size, levels = c("n5", "n10","n15", "n20","n30", "n50"))))
```

As n increases, 
the mean and the std deviation do not change except for n5. 
n50 follows normal distribution as sample size is larger than 

# Exercise 5

1. Null Hypothesis:  mu is 1526.236
   Alternate Hypothesis: mu /NE 1526.236
   

```{r}

#t-score
#p-value


p_tbl <- tibble(p25 = vector())
for (i in seq(1:10000)){
  this_sample <- sample(df3$Retention.index,size = 25)
  this_mean <- mean(this_sample)
  this_sd <- sd(this_sample)
  this_t <- (this_mean-1526.236)/(this_sd/sqrt(25))
  this_p <- 2*pt(-abs(this_t),df=24)
  p_tbl %>%
    add_row(p25 = this_p) -> p_tbl
}
     
```


```{r}
p_tbl %>% 
  ggplot(aes(x=p25))+
  geom_histogram(fill='grey', color='black', bins = sqrt(nrow(p_tbl)))
```
```{r}
p_tbl %>%
  filter(p25<=0.05) -> reject_null
p_tbl %>%
  filter(p25>0.05) -> reject_alt

nrow(reject_alt)/nrow(p_tbl)
nrow(reject_null)/nrow(p_tbl)
```


The proportion of p-values that reject the alternative hypothesis: `r nrow(reject_alt)/nrow(p_tbl)`
The proportion of p-values that reject the null hypothesis : `r nrow(reject_null)/nrow(p_tbl)`



